COSC3500 \\ 2D Orbital Simulation Report

### 2018-10-16 reports/ms1_report.tex
Update report

\section*{Parallelism}
A description of your parallel implementation. How do you make use of OpenMP and MPI? How is information and work shared between threads and processes.  Any optimisations applied and/or challenges encountered will go here.
\subsection*{Implementation}
\subsubsection*{OpenMP}

@@

@@

\includegraphics[width=3cm]{mpi_gather}
\includegraphics[width=3cm]{mpi_scatter}

@@

\begin{enumerate}
    \item The number of bodies ($n$) (\texttt{512, 1024, 2048, 4096, 8192, 16384})
    \item \texttt{ENABLE\_BARNES\_HUT} (\texttt{true, false})
    \item \texttt{--nodes} (\texttt{1, 4, 16})
    \item \texttt{--ntasks} (\texttt{1, 4, 16})
    \item \texttt{--ntasks-per-node} (\texttt{1, 4})
    \item \texttt{--cpus-per-task} (\texttt{1, 4, 16})
\end{enumerate}

>>>>

\section*{Parallelism}
% A description of your parallel implementation. How do you make use of OpenMP and MPI? How is information and work shared between threads and processes.  Any optimisations applied and/or challenges encountered will go here.
\subsection*{Implementation}
\subsubsection*{OpenMP}

@@

\includegraphics[width=7cm]{mpi_scatter}
\includegraphics[width=7cm]{mpi_gather}

@@

\begin{verbatim}
Total CPU time on rank 0 was 89.820000
Total CPU time on rank 2 was 36.750000
Total CPU time on rank 3 was 36.960000
Total CPU time on rank 1 was 37.040000
\end{verbatim}

@@

\begin{enumerate}
    \item The number of bodies ($n$) (\texttt{512, 1024, 2048, 4096, 8192, 16384})
    \item \texttt{ENABLE\_BARNES\_HUT} (\texttt{true, false})
    \item \texttt{--nodes} (\texttt{Disabled, 1, 4, 16})
    \item \texttt{--ntasks} (\texttt{1, 4, 16})
    \item \texttt{--ntasks-per-node} (\texttt{1, 4})
    \item \texttt{--cpus-per-task} (\texttt{1, 4, 16})
    \item \texttt{\#pragma omp parallel schedule(static, dynamic, guided)}
\end{enumerate}
